Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-07 PreregristrationS3/PreregistrationAOT-M.Rmd
moved to subfolder

---
title           : "Psychological Needs During Intergroup Contact: Young Medical Professionals Sample"
shorttitle      : "Preregistration: Needs During Intergroup Contact"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1,2"
  - name        : Maximilian Agostini
    affiliation : "1,2"
  - name        : Laura Bringmann
    affiliation : "1,2"
  - name        : Peter de Jonge
    affiliation : "1,2"
  - name        : Kai Epstude
    affiliation : "1,2"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Author order to be discussed; currently alphabetic by last name.
bibliography: references.bib
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---

>>>>

---
title           : "Psychological Needs During Intergroup Contact: Young Medical Professionals Sample"
shorttitle      : "Preregistration: Needs During Intergroup Contact"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1,2"
  - name        : Maximilian Agostini
    affiliation : "1,2"
  - name        : Laura Bringmann
    affiliation : "1,2"
  - name        : Peter de Jonge
    affiliation : "1,2"
  - name        : Kai Epstude
    affiliation : "1,2"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Author order to be discussed; currently alphabetic by last name.
bibliography: "../references.bib"
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---
